TE_computation

### 2021-06-09 simulations_old_versions/computational model/TE_computation_Simulation.Rmd
organizing folders

>>>>

D_seq = seq(50, 600, by = 25)
N_seq = seq(0, 600, by = 25)

D = rep(D_seq, length(N_seq))
N = rep(N_seq, length(D_seq))

data_Simulation1 <- data.frame(V, D, N) %>%
  arrange(D, N) %>%
  filter(N <= D) %>%
  # Get word vocabulary W
  mutate(W = D + N) %>%
  # Create other variables
  mutate(B = N/(D+N), # balance,
         TE = (D*N)/V) %>% # If D and N are independent, TE = DN/V
  # Round to keep whole numbers only
  mutate_at(vars(-B), round, 0) %>%
  # bin B into 6 groups
  mutate(bin_B = cut(B, breaks = 5, 
                     labels = c("0.1", "0.2", "0.3", "0.4", "0.5"))) %>%
  arrange(W, bin_B)

### 2021-06-09 simulations_old_versions/computational model/old/old_TE_computation_Simulation.Rmd
organizing folders

library(here)
library(tidyverse)
library(tidylog)
library(ggpubr)
library(regclass) # for correlation
library(effects)
# library(jtools)
library(FRACTION) # this allows us to use the is.wholenumber function

@@

# Generating dataframe for computational model
#### Set 1: Calculate other variables based on V, W, and B ####
```{r}
### Generating variables: V, W, and B
## V = 600 ##
# Items on vocabulary measure (e.g. words on the CDI)
V <- 600

# Total word vocabulary of a child
W <- seq(0, 2*V, by = 25)

# Balance, i.e. proportion use of non-dominant language (B ≤ .50)
B <- seq(0.5, 1, by = 0.025)

# Generating sequence of W and B
W_seq <- W %>% # a sequence of 0 to 2V
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>%  # a sequence of 0.5 to 1
  rep(., length(W)) # generate N repetitions of the sequence based on length of W

# Creating the dataframe
TE_V600 <- data.frame(V, W_seq) %>%
  arrange(W_seq) %>%
  rename(W = W_seq) %>%
  mutate(B = B_seq)

## V = 450 ##
# Items on vocabulary measure (e.g. words on the CDI)
V <- 450

# Total word vocabulary of a child
W <- seq(0, 2*V, by = 25)

# Balance, i.e. proportion use of non-dominant language (B ≤ .50)
B <- seq(0.5, 1, by = 0.025)

# Generating sequence of W and B
W_seq <- W %>% # a sequence of 0 to 2V
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>%  # a sequence of 0.5 to 1
  rep(., length(W)) # generate N repetitions of the sequence based on length of W

# Creating the dataframe
TE_V450 <- data.frame(V, W_seq) %>%
  arrange(W_seq) %>%
  rename(W = W_seq) %>%
  mutate(B = B_seq)

## V = 300 ##
# Items on vocabulary measure (e.g. words on the CDI)
V <- 300

# Total word vocabulary of a child
W <- seq(0, 2*V, by = 25)

# Balance, i.e. proportion use of non-dominant language (B ≤ .50)
B <- seq(0.5, 1, by = 0.025)

# Generating sequence of W and B
W_seq <- W %>% # a sequence of 0 to 2V
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>%  # a sequence of 0.5 to 1
  rep(., length(W)) # generate N repetitions of the sequence based on length of W

# Creating the dataframe
TE_V300 <- data.frame(V, W_seq) %>%
  arrange(W_seq) %>%
  rename(W = W_seq) %>%
  mutate(B = B_seq)

## V = 150 ##
# Items on vocabulary measure (e.g. words on the CDI)
V <- 150

# Total word vocabulary of a child
W <- seq(0, 2*V, by = 25)

# Balance, i.e. proportion use of non-dominant language (B ≤ .50)
B <- seq(0.5, 1, by = 0.025)

# Generating sequence of W and B
W_seq <- W %>% # a sequence of 0 to 2V
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>%  # a sequence of 0.5 to 1
  rep(., length(W)) # generate N repetitions of the sequence based on length of W

# Creating the dataframe
TE_V150 <- data.frame(V, W_seq) %>%
  arrange(W_seq) %>%
  rename(W = W_seq) %>%
  mutate(B = B_seq)

### Combining all dataframes and Calculate other variables
TE_fromVWB <- TE_fromVWB <- rbind(TE_V150, TE_V300, TE_V450, TE_V600) %>%
  # Create other variables
  mutate(D = B*W, # Words produced in the dominant language
         N = (1-B)*W, # Words produced in non-dominant language
         TE = (D*N)/V, # If D and N are independent, TE = DN/V
         C = W-TE, # Concept vocabulary (or total conceptual vocabulary size)
         Du = D-TE, # Unique words in dominant language
         Nu = N-TE) %>% # Unique words in non-dominant language
  # In reality, it would be impossible to get negative numbers for any vocabulary variables, so filter out all cases with negative numbers
  filter(Nu >= 0) %>%
  # It is also not possible for D or N to exceed V, so filter out cases where D or N > V
  filter_at(vars(D, N), all_vars(. <= V)) %>%
  # filter out cases where D or N aren't whole numbers
  filter_at(vars(D, N), any_vars(is.wholenumber(.))) 
```

#### Set 2: Calculate other variables based on V, D, and N ####
```{r}
### Generating variables: D and N
## V = 600 ##
V <- 600
D <- seq(0, V, by = 25) 
N <- seq(0, V, by = 25)

# Generating sequence of D and N
D_seq <- D %>% # Words produced in the dominant language
  rep(., length(N)) # generate N repetitions of the sequence based on length of N

N_seq <- N %>% # Words produced in non-dominant language
  rep(., length(D)) # generate N repetitions of the sequence based on length of D

# Creating the dataframe
TE_V600 <- data.frame(V, D_seq) %>%
  arrange(D_seq) %>%
  rename(D = D_seq) %>%
  mutate(N = N_seq)

## V = 450 ##
V <- 450
D <- seq(0, V, by = 25) 
N <- seq(0, V, by = 25)

# Generating sequence of D and N
D_seq <- D %>% # Words produced in the dominant language
  rep(., length(N)) # generate N repetitions of the sequence based on length of N

N_seq <- N %>% # Words produced in non-dominant language
  rep(., length(D)) # generate N repetitions of the sequence based on length of D

# Creating the dataframe
TE_V450 <- data.frame(V, D_seq) %>%
  arrange(D_seq) %>%
  rename(D = D_seq) %>%
  mutate(N = N_seq)

## V = 300 ##
V <- 300
D <- seq(0, V, by = 25) 
N <- seq(0, V, by = 25)

# Generating sequence of D and N
D_seq <- D %>% # Words produced in the dominant language
  rep(., length(N)) # generate N repetitions of the sequence based on length of N

N_seq <- N %>% # Words produced in non-dominant language
  rep(., length(D)) # generate N repetitions of the sequence based on length of D

# Creating the dataframe
TE_V300 <- data.frame(V, D_seq) %>%
  arrange(D_seq) %>%
  rename(D = D_seq) %>%
  mutate(N = N_seq)

## V = 150 ##
V <- 150
D <- seq(0, V, by = 25) 
N <- seq(0, V, by = 25)

# Generating sequence of D and N
D_seq <- D %>% # Words produced in the dominant language
  rep(., length(N)) # generate N repetitions of the sequence based on length of N

N_seq <- N %>% # Words produced in non-dominant language
  rep(., length(D)) # generate N repetitions of the sequence based on length of D

# Creating the dataframe
TE_V150 <- data.frame(V, D_seq) %>%
  arrange(D_seq) %>%
  rename(D = D_seq) %>%
  mutate(N = N_seq)

### Combining all dataframes and Calculate other variables
TE_fromVDN <- rbind(TE_V150, TE_V300, TE_V450, TE_V600) %>%
  # It is not possible for N > D, so keep only cases where D >= N
  filter(D >= N) %>%
  # Create other variables
  mutate(W = D+N, # Total word vocabulary of a child
         B = D/(D+N), # Balance, i.e. proportion use of non-dominant language (B ≤ .50)
         TE = (D*N)/V, # If D and N are independent, TE = DN/V
         C = W-TE, # Concept vocabulary (or total conceptual vocabulary size)
         Du = D-TE, # Unique words in dominant language
         Nu = N-TE) %>%
  # Remove cases where B = NA
  filter(!is.na(B)) 
```

#### Set 3: Calculate other variables based on V, D, and B ####
```{r}
### Creating variables: D and B
## V = 600 #
V <- 600
D <- seq(0, V, by = 25)

D_seq <- D %>% # Words produced in the dominant language
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>% # balance
  rep(., length(D))  # generate N repetitions of the sequence based on length of D

# Creating the dataframe
TE_V600 <- data.frame(V, D_seq) %>%
  arrange(D_seq) %>%
  rename(D = D_seq) %>%
  mutate(B = B_seq)

## V = 450 #
V <- 450
D <- seq(0, V, by = 25)

D_seq <- D %>% # Words produced in the dominant language
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>% # balance
  rep(., length(D))  # generate N repetitions of the sequence based on length of D

# Creating the dataframe
TE_V450 <- data.frame(V, D_seq) %>%
  arrange(D_seq) %>%
  rename(D = D_seq) %>%
  mutate(B = B_seq)

## V = 300 #
V <- 300
D <- seq(0, V, by = 25)

D_seq <- D %>% # Words produced in the dominant language
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>% # balance
  rep(., length(D))  # generate N repetitions of the sequence based on length of D

# Creating the dataframe
TE_V300 <- data.frame(V, D_seq) %>%
  arrange(D_seq) %>%
  rename(D = D_seq) %>%
  mutate(B = B_seq)

## V = 150 #
V <- 150
D <- seq(0, V, by = 25)

D_seq <- D %>% # Words produced in the dominant language
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>% # balance
  rep(., length(D))  # generate N repetitions of the sequence based on length of D

# Creating the dataframe
TE_V150 <- data.frame(V, D_seq) %>%
  arrange(D_seq) %>%
  rename(D = D_seq) %>%
  mutate(B = B_seq)

### Combining all dataframes and Calculate other variables
TE_fromVDB <- rbind(TE_V150, TE_V300, TE_V450, TE_V600) %>%
  # Create other variables
  mutate(W = D/B, # Total word vocabulary of a child
         N = W-D, # Words produced in non-dominant language
         TE = (D*N)/V, # If D and N are independent, TE = DN/V
         C = W-TE, # Concept vocabulary (or total conceptual vocabulary size)
         Du = D-TE, # Unique words in dominant language
         Nu = N-TE) %>% # Unique words in non-dominant language
  # In reality, it would be impossible to get negative numbers for any vocabulary variables, so filter out all cases with negative numbers
  filter(Nu >= 0) %>%
  # It is also not possible for D or N to exceed V, so filter out cases where D or N > V
  filter_at(vars(D, N), all_vars(. <= V)) %>%
  # filter out cases where N isn't whole number
  filter(is.wholenumber(N))
```

#### Set 4: Calculate other variables based on V, N, and B ####
```{r}
### Generating variables: N and B
## V = 600 #
V <- 600
N <- seq(0, V, by = 25)

N_seq <- N %>% # Words produced in the dominant language
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>% # a sequence of 0.5 to 1
  rep(., length(N)) # generate N repetitions of the sequence based on length of N

# Creating the dataframe
TE_V600 <- data.frame(V, N_seq) %>%
  arrange(N_seq) %>%
  rename(N = N_seq) %>%
  mutate(B = B_seq)

## V = 450 #
V <- 450
N <- seq(0, V, by = 25)

N_seq <- N %>% # Words produced in the dominant language
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>% # a sequence of 0.5 to 1
  rep(., length(N)) # generate N repetitions of the sequence based on length of N

# Creating the dataframe
TE_V450 <- data.frame(V, N_seq) %>%
  arrange(N_seq) %>%
  rename(N = N_seq) %>%
  mutate(B = B_seq)

## V = 300 #
V <- 300
N <- seq(0, V, by = 25)

N_seq <- N %>% # Words produced in the dominant language
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>% # a sequence of 0.5 to 1
  rep(., length(N)) # generate N repetitions of the sequence based on length of N

# Creating the dataframe
TE_V300 <- data.frame(V, N_seq) %>%
  arrange(N_seq) %>%
  rename(N = N_seq) %>%
  mutate(B = B_seq)

## V = 150 #
V <- 150
N <- seq(0, V, by = 25)

N_seq <- N %>% # Words produced in the dominant language
  rep(., length(B)) # generate N repetitions of the sequence based on length of B

B_seq <- B %>% # a sequence of 0.5 to 1
  rep(., length(N)) # generate N repetitions of the sequence based on length of N

# Creating the dataframe
TE_V150 <- data.frame(V, N_seq) %>%
  arrange(N_seq) %>%
  rename(N = N_seq) %>%
  mutate(B = B_seq)

### Combining all dataframes and Calculate other variables
TE_fromVNB <- rbind(TE_V150, TE_V300, TE_V450, TE_V600) %>%
  # Create other variables
  mutate(W = D/(1-B), # Total word vocabulary of a child
         D = W-N, # Words produced in dominant language
         TE = (D*N)/V, # If D and N are independent, TE = DN/V
         C = W-TE, # Concept vocabulary (or total conceptual vocabulary size)
         Du = D-TE, # Unique words in dominant language
         Nu = N-TE) %>% # Unique words in non-dominant language
  # It is not possible for N > D, so keep only cases where D >= N
  filter(D >= N) %>%
  # In reality, it would be impossible to get negative numbers for any vocabulary variables, so filter out all cases with negative numbers
  filter(Nu >= 0) %>%
  # It is also not possible for D or N to exceed V, so filter out cases where D or N > V
  filter_at(vars(D, N), all_vars(. <= V)) %>%
  # filter out cases where D isn't whole number
  filter(is.wholenumber(D)) %>%
  filter_at(vars(TE, C, Du, Nu), any_vars(is.wholenumber(.))) %>%
  filter(is.wholenumber(Nu)) 
```

#### Combine the 4 sets ####
```{r}
TE_computation <- TE_fromVWB %>%
  bind_rows(TE_fromVDN, TE_fromVDB, TE_fromVNB) %>%
  # constrain all variables but B (balance) to be integers 
  filter_at(vars(TE, C, Du, Nu), any_vars(is.wholenumber(.)))
```

# Correlation
```{r}
Correlation <- TE_computation %>%
  cor_matrix()

library(Hmisc)
mycor <- rcorr(as.matrix(TE_computation), type="pearson")
mycor$r
mycor$P

library(corrplot)
mycor <- cor(TE_computation)
corrplot(mycor)
#write.table(Correlation, "TEcomputation_correlations.tsv", col.names=NA)
```

@@

ggsave("plot_words.png", plot_words,
       width = 10, height = 5)
```

## Plotting relations between TEs and different variables
##### Relation between TE & W, D, & N #####
```{r}
### Plot: Y = TE, X = D / N
plot_TEandWDN <- TE_computation %>%
  pivot_longer(c(W, D, N, C, Du, Nu), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type %in% c("W", "D", "N")) %>%
  mutate(vocab_type = factor(vocab_type, levels=c("W", "D", "N"))) %>%
  #mutate(bin_B = cut(B, breaks = 6, 
  #                   labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  ggplot(aes(x = number, y = TE)) +
  facet_grid(. ~vocab_type) +
  labs(x = "Words produced", y = "Total number of TEs") +
  geom_point(shape = 23) +
  geom_smooth(method="lm", se=F) +
  scale_y_continuous(limits = c(0, 600)) +
  theme_minimal()

>>>>

library(here)
library(tidyverse)
library(tidylog)
library(ggpubr)
#library(regclass) # for correlation
#library(effects)
# library(jtools)
#library(FRACTION) # this allows us to use the is.wholenumber function

@@

# Read in data
```{r}
TE_computation <- read.csv(here::here("computational model/TE_computation.csv"))
```

# Simulation 1
## Infants of the same developmental level with different word vocabularies and balances of exposure
### V = 600
```{r}
Simulation1 <- TE_computation %>%
  # V = 600
  filter(V == 600) %>%
  # Convert to long data
  pivot_longer(c(W, D, N, C, Du, Nu), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type == c("W", "D", "N")) %>%
  mutate(vocab_type = factor(vocab_type, levels=c("W", "D", "N"))) %>%
  mutate(vocab_type = recode(vocab_type, 
                             W = "Panel A: Total vocabulary (W)", 
                             D = "Panel B: Dominant vocabulary (D)", 
                             N = "Panel C: Non-dominant vocabulary (N)")) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  #mutate(bin_W = cut_interval(W, 12,
  #                   labels = c(100,200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200))) %>%
  ggplot(aes(x = number, y = TE, color = bin_B)) +
  #geom_point() +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ vocab_type) +
  ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Number of words", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)"
       #, title = "Number of translation equivalent by balance in relation to different input measures "
       ) +
  guides(colour = guide_legend(nrow = 1))

ggsave("plot_Simulation1.png", plot_inputs_TE,
       width = 10, height = 5)

# Simulation 2
## Patterns of translation equivalent learning as a function of different developmental timepoints
```{r}
timepoints <- c(150, 300, 450, 600)

Simulation2 <- TE_computation %>%
  filter(V %in% timepoints) %>%
  pivot_longer(c(D, N, TE, C, Du, Nu), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type %notin% c("D", "N", "C")) %>%
  mutate(vocab_type = factor(vocab_type, levels=c("Nu", "Du", "TE"))) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  group_by(V, bin_B, vocab_type) %>%
  summarise(n_words = mean(number)) %>%
  ggplot(aes(x = bin_B, y = n_words, fill = vocab_type)) + 
  geom_bar(position="stack", stat="identity") +
  facet_grid(. ~ V) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) + 
  #scale_y_continuous(limits = c(0, 1200)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90), legend.position = "bottom",
        plot.title = element_text(hjust = 0.5)) + 
  labs(x = "Balance", 
       y = "Number of concepts", 
       title = "Vocabulary composition across different developmental timepoints (V)")

ggsave("plot_Simulation2.png", plot_composition_byV,
        width = 10, height = 5)

# Simulation 3
## Non-independence of dominant-language (D) and non-dominant language words (N)
```{r}

# I * (D*N/V)
I1 = 1.5
I2 = 0.5

Simulation3 <- TE_computation %>%
  filter(V==600) %>%
  ## Calculate where I > 1
  mutate(TE_easier = I1*(D*N/V)) %>%
  ## Calculate where I < 1
  mutate(TE_harder = I2*(D*N/V)) %>%
  pivot_longer(c(TE, TE_harder, TE_easier), 
               names_to = "Model", values_to = "number_TE") %>%
  mutate(Model = factor(Model, levels=c("TE_harder", "TE", "TE_easier"))) %>%
  mutate(Model = recode(Model, 
                        TE = "I = 1 (assuming independence of D and N)",
                        TE_easier = "I = 1.5 (TEs are more easily learned)",
                        TE_harder = "I = 0.5 (TE are less easily learned)")) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  ggplot(aes(x = W, y = number_TE, color = bin_B)) +
  #geom_point() +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ Model) +
  ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Total word vocabulary (W)", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)") +
  guides(colour = guide_legend(nrow = 1))

ggsave("plot_Simulation3.png", Simulation3, 
       width = 10, height = 5)

#Simulation3 <- TE_computation %>%
#  pivot_longer(c(TE_harder, TE_easier), 
#               names_to = "Nonindependence_type", values_to = "Simulated_TEs") %>%
#  mutate(Nonindependence_type = recode(Nonindependence_type, 
#                                       TE_easier = "I = 1.5 (TEs are more easily learned)",
#                                       TE_harder = "I = 0.5 (TE are less easily learned)")) %>%
#  ggplot(aes(y = Simulated_TEs, x = TE, color = Nonindependence_type)) +
#  geom_smooth(method = "lm", se = F) +
#  geom_point(shape = 23) +
#  geom_abline(linetype = 2, alpha = 0.5) +
#  labs(y = "Simulated number of TEs assuming non-independence of D and N", 
#       x = "Expected number of TEs assuming independence of D and N",
#       color = "Scenarios"
#       #, title = "Non-independence vs. Independence of dominant and non-dominant words"
#       ) +
#  theme(plot.title = element_text(hjust = 0.5)) +
#  theme_minimal()

##ggsave("plot_Simulation3.png", Simulation3, 
##       width = 8, height = 6)

@@

ggsave("plot_words.png", plot_words,
       width = 10, height = 5)

plot_inputs <- TE_computation %>%
  # Convert to long data
  pivot_longer(c(W, D, N, TE, C, Du, Nu), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type == c("W", "D", "N", "TE")) %>%
  mutate(vocab_type = as.factor(vocab_type)) %>%
  mutate(vocab_type = fct_relevel(vocab_type, "W")) %>%
  mutate(vocab_type = recode(vocab_type, W = "Total vocabulary (W)", D = "Dominant vocabulary (D)", 
                             N = "Non-dominant vocabulary (N)", TE = "Translation equivalents (TE)")) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  #mutate(bin_W = cut_interval(W, 12,
  #                   labels = c(100,200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1200))) %>%
  group_by(V, bin_B, vocab_type) %>%
  summarise(n_words = mean(number)) %>%
  ggplot(aes(x = V, y = n_words, color = bin_B)) +
  #geom_point() +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ vocab_type) +
  #ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Different timepoints = Learnable vocaobulary (V)", 
       y = "Number of words", 
       color = "Balance",
       title = "Word vocabulary size by balance under different input measures and translation equivalents") +
  guides(colour = guide_legend(nrow = 1))

ggsave("plot_inputs.png", plot_inputs,
       width = 10, height = 5)

plot_inputs_TE_V <- TE_computation %>%
  filter(W == 250) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  ggplot(aes(x = V, y = TE, color = bin_B)) +
  #geom_point() +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  #facet_grid(. ~ bin_W) +
  #ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Developmental timepoint (V)", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)") +
  guides(colour = guide_legend(nrow = 1))

plot_inputs_TE_V <- TE_computation %>%
  filter(W == 400) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  #mutate(bin_W = cut_interval(W, 3,
  #                   labels = c("W = 0 - 400" , "W = 401 - 800", "W = 801 - 1200"))) %>%
  ggplot(aes(x = V, y = TE, color = bin_B)) +
  #geom_point() +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  #facet_grid(. ~ bin_B) +
  #ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Developmental timepoint (V)", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)") +
  guides(colour = guide_legend(nrow = 1))

ggsave("plot_inputs_TE_V.png", plot_inputs_TE_V,
       width = 6, height = 6)

plot_inputs_TE_V <- TE_computation %>%
  #filter(W == 100) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  mutate(bin_W = cut_interval(W, 4,
                     labels = c("W = 0 - 300" , "W = 301 - 600", "W = 601 - 900", "W = 901 - 1200"))) %>%
  ggplot(aes(x = V, y = TE, color = bin_W)) +
  #geom_point() +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ bin_B) +
  #ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Developmental timepoint (V)", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)") +
  guides(colour = guide_legend(nrow = 1))

ggsave("plot_inputs_TE_V.png", plot_inputs_TE_V,
       width = 10, height = 5)

## Plotting different scenarios
```{r}
plot_scenarios <- TE_computation %>%
  pivot_longer(c(D, N, TE, C, Du, Nu), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type == c("D", "N", "TE")) %>%
  mutate(vocab_type = factor(vocab_type, levels=c("N", "D", "TE"))) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  group_by(V, bin_B, vocab_type) %>%
  summarise(n_words = mean(number)) %>%
  ggplot(aes(x = bin_B, y = n_words, fill = vocab_type)) + 
  geom_bar(position="stack", stat="identity") +
  facet_grid(. ~ V) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) + 
  #scale_y_continuous(limits = c(0, 1200)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90), legend.position = "bottom") + 
  labs(x = "Balance", 
       y = "Number of words (W)", 
       title = "Vocabulary composition across different developmental timepoints (V)")

## Plotting relations between TEs and different variables
##### Relation between TE & W, D, & N #####
```{r}
### Plot: Y = TE, X = D / N
plot_TEandWDN <- TE_computation %>%
  pivot_longer(c(W, D, N, C, Du, Nu), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type %in% c("W", "D", "N")) %>%
  mutate(vocab_type = factor(vocab_type, levels=c("W", "D", "N"))) %>%
  ggplot(aes(x = number, y = TE)) +
  facet_grid(. ~ vocab_type) +
  labs(x = "Words produced", y = "Total number of TEs") +
  #geom_point(shape = 23) +
  geom_smooth(method="lm", se=F) +
  scale_y_continuous(limits = c(0, 600)) +
  theme_minimal()
